Supplemental Online Materials

### 2023-05-31 Documents/manuscript.tex
submit

@@

In this paper, we examine double standards in judging collective
action---that is, whether observers judge the same protest actions as
more or less acceptable depending on their own and the protesters' group
memberships (\emph{identity-based double standards}) or on the
protesters' cause and how it aligns with their own ideological positions
(\emph{ideology-based double standards}). In two studies, we first
develop an instrument of 25 controversial protest actions, based in item
response theory, to capture double standards in judging collective
action. In three preregistered experiments, we then use this instrument
to test for double standards in judging protest actions for workers'
rights in the United Kingdom and for or against defunding the police and
for or against restricting abortion in the United States. We find
evidence for ideology-based, but not for identity-based, double
standards: People judge the same protest actions to be more acceptable
when the protesters' cause aligns with their own ideological
positions---but do not show consistent ingroup bias (in terms of class,
race, and gender) when judging collective action by ingroup and outgroup
members.

@@

In this research, we move this distinction from the researcher's
intuition into the realm of scientific investigation and test for double
standards in where people draw the line between acceptable (normative)
and unacceptable (non-normative) forms of collective action. For that
purpose, we define a double standard as judging the same protest actions
as more or less acceptable depending on who the protesters are and what
they are protesting. (for an analogous definition, see Foschi,
2000).\footnote{Feinberg et al. (2020) provided incidental evidence for
  double standards in judging collective action as, in a manipulation
  check, Black participants rated Black Lives Matter protests as less
  extreme than White participants and liberal participants rated protest
  actions for progressive causes as less extreme than conservative
  participants.}

@@

Partisan differences can result from two social psychological processes.
On the one hand, political partisanship reflects ideological differences
in resistance to social change and acceptance of inequality which, in
turn, are motivated by epistemic, existential, and relational needs
(Jost et al., 2003; Jost, 2021). As motivated cognition, ideological
orientations shape how we think and feel about issues, actions, and
events. On the other hand, political partisanship functions as a social
identity (Finkel et al., 2020; Harris et al., 2022) with evidence
suggesting that partisans' policy preferences depend more on the stated
position of their party than policy content (Cohen, 2003). Like other
identities, political identities result in group-serving biases in how
we evaluate ingroup and outgroup members. In practice, the two processes
are often difficult to disentangle.

@@

The second purpose of our research is to test for double standards in
judging collective action---that is, whether people judge the same
protest actions as more acceptable if the protesters' are ingroup
members or the protesters' cause aligns with the ingroup's interests
(\emph{Hypothesis 1a}, \emph{1b}) or if the protesters' cause aligns
with their own system-justifying or system-challenging motives
(\emph{Hypotheses 2a}, \emph{2b}). In Experiment 1, we use the
instrument developed in Studies 1 and 2 to test for double standards in
how acceptable participants consider collective action for workers'
rights in the United Kingdom. By varying both the participants' and the
protesters' group memberships (working/middle class), Experiment 1
compares the relative evidence for identity-based (\emph{Hypothesis 1a},
\emph{1b}) and ideology-based double standards (\emph{Hypothesis 2a}).
Extending Experiment 1, Experiment 2 considers both system-challenging
and system-defending collective action in the context of the 2020 Black
Lives Matter protests in the United States. By varying the protesters'
cause (for/against defunding the police) as well as the participants'
and the protesters' group memberships (Black/White), Experiment 2
compares the relative evidence for identity-based (\emph{Hypothesis 1a},
\emph{1b}) and ideology-based double standards (\emph{Hypothesis 2a},
\emph{2b}). Building on Experiments 1--2, Experiment 3 examines how
liberal and conservative men and women judge collective action for or
against restricting abortion in anticipation of the Supreme Court
overturning its \emph{Roe v. Wade} decision on reproductive rights in
the United States. By varying the protesters' cause as well as the
participants' ideology and gender, Experiment 3 compares the relative
evidence for identity-based (\emph{Hypothesis 1b}) and ideology-based
(\emph{Hypothesis 2b}) double standards in judging collective action
concerning a conservative cause in a sample balanced by gender and
ideology. Together, the preregistered experiments provide a
comprehensive test of the hypothesized double standards in judging
collective action.

@@

Model 1 (M1) estimated varying intercepts for the eight conditions to
test whether, in line with Hypotheses 1a, 1b, or 2a, participants'
responses depended on their own group membership, the protesters' group
membership, or the protesters' cause. Contradicting \emph{Hypothesis
1a}, participants did not consider protest actions performed by their
ingroup to be more acceptable, on average, than the same actions
performed by the relevant outgroup (\(d = 0.01, [-0.04, 0.06]\)).
Contradicting \emph{Hypothesis 1b}, participants did not consider
protest actions for a cause that was nominally aligned with their
ingroup's interests to be more acceptable, on average, than protest
actions for a cause not aligned with their ingroup's interests
(\(d = -0.01, [-0.06, 0.04]\)). Contradicting \emph{Hypothesis 2a},
participants did not consider protest actions for a system-defending
cause to be more acceptable, on average, than protest actions for a
system-challenging cause (\(d = -0.14, [-0.20, -0.09]\)). Instead, we
found that, on average, White participants considered all protest
actions to be more acceptable than Black participants
(\(d = 0.09, [0.04, 0.14]\)) and both Black (\(d = 0.13, [0.06, 0.20]\))
and White (\(d = 0.16, [0.08, 0.23]\)) participants considered the same
actions to be more acceptable when protests were for, rather than
against, defunding the police. As in Experiment 1, we thus found that
participants' responses depended on both the participants' and the
protesters' group memberships---but not in the directions predicted by
our hypotheses.

Model 2 (M2) extended Model 1 by estimating participants' responses as a
function of their \emph{z}-standardized endorsement of system-justifying
beliefs. As preregistered, we modeled this relationship with two fixed
effects, one estimating the effect of system-justifying beliefs on
judgments about system-defending protest actions and one estimating
their effect on judgments about system-challenging protest actions, and
one varying effect estimating its variance across conditions. Supporting
\emph{Hypothesis 2b}, participants who \emph{rejected} system-justifying
beliefs were \emph{more} likely to consider system-challenging protest
actions (for defunding the police) to be acceptable means of protest
(\(\beta_{xy} = 0.38, [0.16, 0.58]\)). We did not, however, find
evidence for the ideological symmetry implied by \emph{Hypothesis 2b}
since participants who \emph{endorsed} system-justifying beliefs were
\emph{not} more likely to consider system-defending protest actions
(against defunding the police) to be acceptable means of protest
(\(\beta_{xy} = -0.18, [-0.40, 0.02]\)).

@@

Model 3 (M3) extended Model 1 by estimating participants' responses as a
function of their self-reported support for the cause of the protest. We
recoded participants' responses to create a predictor variable that
encoded support for defunding the police when protesters supported
defunding the police and opposition to defunding the police when
protesters opposed defunding the police. As preregistered, we modeled
this relationship as a monotonic effect (Bürkner \& Charpentier, 2020)
that estimated the average change in the outcome variable across
predictor categories as well as how much of this change occurred between
each of the four pairs of adjacent predictor categories.\footnote{Our
  model assigned a Dirichlet prior, \(\alpha = {1, 1, 1, 1}\), to the
  proportions of the overall change that was expected to occur between
  each of the four pairs of predictor categories.} Contradicting
\emph{Hypothesis 3}, participants who supported the protesters' cause
did not, on average, consider the same protest actions to be more
acceptable than participants who opposed the protesters' cause
(\(\beta_{y} = 0.14, [-0.12, 0.40]\)). Ergo, our results did not support
the alternative hypothesis that ideology-based double standards can be
reduced to support for, or opposition to, the cause of a protest.

@@

We explored whether group identification moderated how the participants'
and the protesters' group memberships affected participants' responses.
To that end, we extended Model 1 by estimating participants' responses
as a function of their \emph{z}-standardized identification with their
racial ingroup. As in Model 2, we modeled this relationship with a fixed
and a varying effect. We found, however, that even participants who
strongly identified with their racial ingroup (+1\emph{SD}) did not
consider protest actions performed by their ingroup to be more
acceptable than the same actions performed by the relevant outgroup
(\(d = 0.01, [-0.00, 0.02]\)) and did not consider protest actions for a
cause that was aligned with their ingroup's interests to be more
acceptable than protest actions for a cause not aligned with their
ingroup's interests (\(d = 0.00, [-0.01, 0.01]\)). Our non-preregistered
analyses thus suggested that group identification did not moderate group
differences in judgments about collective action by ingroup and outgroup
members.

@@

\noindent As in the previous experiments, participants rated which of
several protest actions they consider acceptable means to protest for or
against restricting abortion. On the next pages, participants completed
the remaining measures. On the final page, participants responded to two
attention checks that assessed whether they paid attention to the
experimental manipulation: ``In this study, you read about some people's
view on a policy change. What was the policy change?'' and ``In this
study, you then read about some protesters. Were the protesters for or
against restricting abortion?''.

@@

Growing evidence shows that, in many situations, observers apply a more
lenient standards when judging moral transgressions by ingroup members
(Abrams et al., 2013; Endevelt et al., 2021). And yet, our findings
suggested that, unlike judgments in other domains, judgments about
collective action are not subject to double standards based on group
identities such as class, race, or gender. We did not find evidence for
those double standards even though we examined social categories that
are central to most people's identities, even when we considered only
highly identified group members, and even though participants' reactions
to the manipulation showed that, at least in Experiments 1--2, they
understood the protesters' causes in ingroup--outgroup terms.

@@

First, we might understand ideology-based double standards as an
expression of ingroup bias based on opinion-based (McGarty et al., 2009)
or partisan (Finkel et al., 2020; Harris et al., 2022) identities. This
explanation aligns with Verkuyten et al.'s (2022) finding that
participants were more tolerant of transgressive protest actions when
taken by their most-liked, rather than their least-liked, political
group (e.g., climate activists). An identity-based account, however,
implies that both conservatives and progressives would show ingroup bias
and, therefore, cannot explain the observed asymmetry in the two groups'
double standards.

@@

Lastly, we might consider that collective action, even in its
controversial forms, is not judged as a moral transgression (as in
previous research on identity-based double standards, e.g., Abrams et
al., 2013)---but is instead understood as a means to an end and judged
in relation to its end (``the end justifies the mean''). Their different
moral concerns (Graham et al., 2009; Kivikangas et al., 2021) might lead
progressives and conservatives to see their support of certain causes as
a fundamental matter of right or wrong (Skitka et al., 2021) and, by
thus moralizing those causes, to accept more extreme means to achieving
them. This explanation aligns with Richardson \& Conway's (2022) finding
that moral concerns explained why liberals rated protesting for liberal
causes as more moral than conservatives (and vice versa). A values-based
account could also explain why conservatives who, more so than liberals,
endorse moral concerns related to loyalty and authority tend to reject
disruptive protest actions even when the protesters' cause otherwise
aligns with their moral concerns.

>>>>

\vfill

\begin{center}
\noindent 11,546 words
\end{center}

\vfill

\section{Public Significance Statement}

\noindent This research shows that what people consider an acceptable
\emph{means} of protest depends on what the \emph{end} of a protest is.
That is, people tend to judge the \emph{same} controversial protest
actions to be more acceptable when the protesters' cause aligned with
their own ideological positions. This finding helps explain the often
divided response to recent protest movements.

@@

In this paper, we examine double standards in judging collective
action---that is, whether observers judge the same protest actions as
more or less acceptable depending on their own and the protesters' group
memberships (\emph{identity-based double standards}) or on the
protesters' cause and how it aligns with their own ideological positions
(\emph{ideology-based double standards}). In two studies, we first
develop an instrument of 25 controversial protest actions, based in item
response theory, to capture double standards in judging collective
action. In three preregistered experiments, we then use this instrument
to test for double standards in judging protest actions for workers'
rights, for or against defunding the police, and for or against
restricting abortion. We find evidence for ideology-based, but not for
identity-based, double standards: People judge the same protest actions
to be more acceptable when the protesters' cause aligns with their own
ideological positions---but do not show consistent ingroup bias (in
terms of class, race, and gender) when judging collective action by
ingroup and outgroup members.

@@

In this research, we move this distinction from the researcher's
intuition into the realm of scientific investigation and test for double
standards in where people draw the line between acceptable (normative)
and unacceptable (non-normative) forms of collective action. For that
purpose, we define a double standard as judging the same protest actions
as more or less acceptable depending on who the protesters are and what
they are protesting (for an analogous definition, see Foschi,
2000).\footnote{Feinberg et al. (2020) provided incidental evidence for
  double standards in judging collective action as, in a manipulation
  check, Black participants rated Black Lives Matter protests as less
  extreme than White participants and liberal participants rated protest
  actions for progressive causes as less extreme than conservative
  participants.}

@@

Partisan differences can result from two social psychological processes.
On the one hand, political partisanship reflects ideological differences
in resistance to social change and acceptance of inequality which, in
turn, are motivated by epistemic, existential, and relational needs
(Jost et al., 2003; Jost, 2021). As motivated cognition, ideological
differences shape how we think and feel about issues, actions, and
events. On the other hand, political partisanship functions as a social
identity (Finkel et al., 2020; Harris et al., 2022) with evidence
suggesting that partisans' policy preferences depend more on the stated
position of their party than policy content (Cohen, 2003). Like other
identities, political identities result in group-serving biases in how
we evaluate ingroup and outgroup members. In practice, the two processes
are often difficult to disentangle.

@@

The second purpose of our research is to test for double standards in
judging collective action---that is, whether people judge the same
protest actions as more acceptable if the protesters' are ingroup
members or the protesters' cause aligns with the ingroup's interests
(\emph{Hypothesis 1a}, \emph{1b}) or if the protesters' cause aligns
with their own system-justifying or system-challenging motives
(\emph{Hypotheses 2a}, \emph{2b}).

In Experiment 1, we use the instrument developed in Studies 1 and 2 to
test for double standards in how acceptable participants consider
collective action for workers' rights in the United Kingdom. By varying
both the participants' and the protesters' group memberships
(working/middle class), Experiment 1 compares the relative evidence for
identity-based (\emph{Hypothesis 1a}, \emph{1b}) and ideology-based
double standards (\emph{Hypothesis 2a}). Extending Experiment 1,
Experiment 2 considers both system-challenging and system-defending
collective action in the context of the 2020 Black Lives Matter protests
in the United States. By varying the protesters' cause (for/against
defunding the police) as well as the participants' and the protesters'
group memberships (Black/White), Experiment 2 compares the relative
evidence for identity-based (\emph{Hypothesis 1a}, \emph{1b}) and
ideology-based double standards (\emph{Hypothesis 2a}, \emph{2b}).
Building on Experiments 1--2, Experiment 3 examines how liberal and
conservative men and women judge collective action for or against
restricting abortion in anticipation of the Supreme Court overturning
its \emph{Roe v. Wade} decision on reproductive rights in the United
States. By varying the protesters' cause as well as the participants'
ideology and gender, Experiment 3 compares the relative evidence for
identity-based (\emph{Hypothesis 1b}) and ideology-based
(\emph{Hypothesis 2b}) double standards in judging collective action
concerning a conservative cause in a sample balanced by gender and
ideology. Together, the preregistered experiments provide a
comprehensive test of the hypothesized double standards in judging
collective action.

@@

Model 1 estimated varying intercepts for the eight conditions to test
whether, in line with Hypotheses 1a, 1b, or 2a, participants' responses
depended on their own group membership, the protesters' group
membership, or the protesters' cause. Contradicting \emph{Hypothesis
1a}, participants did not consider protest actions performed by their
ingroup to be more acceptable, on average, than the same actions
performed by the relevant outgroup (\(d = 0.01, [-0.04, 0.06]\)).
Contradicting \emph{Hypothesis 1b}, participants did not consider
protest actions for a cause that was nominally aligned with their
ingroup's interests to be more acceptable, on average, than protest
actions for a cause not aligned with their ingroup's interests
(\(d = -0.01, [-0.06, 0.04]\)). Contradicting \emph{Hypothesis 2a},
participants did not consider protest actions for a system-defending
cause to be more acceptable, on average, than protest actions for a
system-challenging cause (\(d = -0.14, [-0.20, -0.09]\)). Instead, we
found that, on average, White participants considered all protest
actions to be more acceptable than Black participants
(\(d = 0.09, [0.04, 0.14]\)) and both Black (\(d = 0.13, [0.06, 0.20]\))
and White (\(d = 0.16, [0.08, 0.23]\)) participants considered the same
actions to be more acceptable when protests were for, rather than
against, defunding the police. As in Experiment 1, we thus found that
participants' responses depended on both the participants' and the
protesters' group memberships---but not in the directions predicted by
our hypotheses.

Model 2 extended Model 1 by estimating participants' responses as a
function of their \emph{z}-standardized endorsement of system-justifying
beliefs. As preregistered, we modeled this relationship with two fixed
effects, one estimating the effect of system-justifying beliefs on
judgments about system-defending protest actions and one estimating
their effect on judgments about system-challenging protest actions, and
one varying effect estimating its variance across conditions. Supporting
\emph{Hypothesis 2b}, participants who \emph{rejected} system-justifying
beliefs were \emph{more} likely to consider system-challenging protest
actions (for defunding the police) to be acceptable means of protest
(\(\beta_{xy} = 0.38, [0.16, 0.58]\)). We did not, however, find
evidence for the ideological symmetry implied by \emph{Hypothesis 2b}
since participants who \emph{endorsed} system-justifying beliefs were
\emph{not} more likely to consider system-defending protest actions
(against defunding the police) to be acceptable means of protest
(\(\beta_{xy} = -0.18, [-0.40, 0.02]\)).

@@

Model 3 extended Model 1 by estimating participants' responses as a
function of their self-reported support for the cause of the protest. We
recoded participants' responses to create a predictor variable that
encoded support for defunding the police when protesters supported
defunding the police and opposition to defunding the police when
protesters opposed defunding the police. As preregistered, we modeled
this relationship as a monotonic effect (Bürkner \& Charpentier, 2020)
that estimated the average change in the outcome variable across
predictor categories as well as how much of this change occurred between
each of the four pairs of adjacent predictor categories.\footnote{Our
  model assigned a Dirichlet prior, \(\alpha = {1, 1, 1, 1}\), to the
  proportions of the overall change that was expected to occur between
  each of the four pairs of predictor categories.} Contradicting
\emph{Hypothesis 3}, participants who supported the protesters' cause
did not, on average, consider the same protest actions to be more
acceptable than participants who opposed the protesters' cause
(\(\beta_{y} = 0.14, [-0.12, 0.40]\)). Ergo, our results did not support
the alternative hypothesis that ideology-based double standards can be
reduced to support for, or opposition to, the cause of a protest.

@@

We explored whether group identification moderated how the participants'
and the protesters' group memberships affected participants' responses.
To that end, we extended Model 1 by estimating participants' responses
as a function of their \emph{z}-standardized identification with their
racial ingroup. As in Model 2, we modeled this relationship with a fixed
and a varying effect. We found, however, that even participants who
strongly identified with their racial ingroup (+1\emph{SD}) did not
consider protest actions performed by their ingroup to be more
acceptable than the same actions performed by the relevant outgroup
(\(d = 0.05, [-0.01, 0.13]\)) and did not consider protest actions for a
cause that was aligned with their ingroup's interests to be more
acceptable than protest actions for a cause not aligned with their
ingroup's interests (\(d = 0.01, [-0.06, 0.08]\)). Our non-preregistered
analyses thus suggested that group identification did not moderate group
differences in judgments about collective action by ingroup and outgroup
members.

@@

\noindent As in the previous experiments, participants rated which of
several protest actions they consider acceptable means to protest for or
against restricting abortion. On the next pages, participants completed
the remaining measures. On the final page, participants responded to two
attention checks that assessed whether they had paid attention to the
experimental manipulation: ``In this study, you read about some people's
view on a policy change. What was the policy change?'' and ``In this
study, you then read about some protesters. Were the protesters for or
against restricting abortion?''.

@@

Growing evidence shows that, in many situations, observers apply a more
lenient standard when judging moral transgressions by ingroup members
(Abrams et al., 2013; Endevelt et al., 2021). And yet, our findings
suggested that, unlike judgments in other domains, judgments about
collective action are not subject to double standards based on group
identities such as class, race, or gender. We did not find evidence for
those double standards even though we examined social categories that
are central to most people's identities, even when we considered only
highly identified group members, and even though participants' reactions
to the manipulation showed that, at least in Experiments 1--2, they
understood the protesters' causes in ingroup--outgroup terms.

@@

First, we might understand ideology-based double standards as an
expression of ingroup bias based on opinion-based (McGarty et al., 2009)
or partisan (Finkel et al., 2020; Harris et al., 2022) identities. This
explanation aligns with Verkuyten et al.'s (2022) finding that
participants were more tolerant of transgressive protest actions when
taken by their most-liked, rather than their least-liked, political
group (e.g., climate activists). An identity-based account, however,
implies that both conservatives and progressives would show ingroup bias
and, therefore, cannot explain the observed asymmetry in the two groups'
judgements.

@@

Lastly, we might consider that collective action, even in its
controversial forms, is not judged as a moral transgression (as in
previous research on identity-based double standards, e.g., Abrams et
al., 2013)---but is instead understood as a means to an end and judged
in relation to its end (``the end justifies the means''). Their
different moral concerns (Graham et al., 2009; Kivikangas et al., 2021)
might lead progressives and conservatives to see their support of
certain causes as a fundamental matter of right or wrong (Skitka et al.,
2021) and, by thus moralizing those causes, to accept more extreme means
to achieving them. This explanation aligns with Richardson and Conway's
(2022) finding that moral concerns explained why liberals rated
protesting for liberal causes as more moral than conservatives (and vice
versa). A values-based account could also explain why conservatives who,
more so than liberals, endorse moral concerns related to loyalty and
authority tend to reject disruptive protest actions even when the
protesters' cause otherwise aligns with their moral concerns.

### 2023-05-31 Documents/supplemental-materials.qmd
submit

# Reanalysis of Teixeira et al.'s [-@teixeira_white_2022] experiment

At the height of the 2020 Black Lives Matter protests, @teixeira_white_2022 exposed White Americans ($N = 399$) to photos of either peaceful or destructive Black Lives Matter protests and asked them to rate how legitimate (i.e., fair, reasonable, legitimate, and justified) they thought the pictured protests were. As such, their findings make for an interesting comparison to our findings. @teixeira_white_2022, however, reported results from a linear model estimating the three-way interaction between the experimental manipulation, belief in systemic racial injustice, and group identification while controlling for political orientation. This analysis did not provide a direct comparison to our findings.

To compare theirs to our findings, we instead estimated a series of simpler linear regression models, using the brms R package [@burkner_brms_2017; @burkner_advanced_2018] and weakly informative Student-*t* $(3, 0, 2.5)$ prior distributions, with participants' ratings of how legitimate the pictured protests were as the outcome variable.^[We thank the authors for making their data available online ([https://osf.io/sud2y/](https://osf.io/sud2y/)).] First, we found that, as expected, participants considered peaceful protests far more legitimate than destructive protests ($\text{Cohen's}~d = 1.14, [0.98, 1.30]$). Second, we found that more conservative participants rated destructive protests ($\beta_{xy} = -0.59, [-0.68, -0.49]$) and, to a lesser extent, peaceful protests ($\beta_{xy} = -0.20, [-0.30, -0.10]$) to be less legitimate than more liberal participants. Third, we found that participants who identified more strongly with their (White American) ethnic identity rated destructive protests ($\beta_{xy} = -0.35, [-0.45, -0.24]$) and, to a lesser extent, peaceful protests ($\beta_{xy} = -0.10, [-0.21, 0.01]$) to be less legitimate than participants who identified less strongly with their (White American) ethnic identity. Finally, we found that participants' group identification was no longer associated with how legitimate they rated peaceful ($\beta_{xy} = -0.02, [-0.13, 0.05]$) and destructive ($\beta_{xy} = -0.06, [-0.17, 0.05]$) protests to be after controlling for their political orientation. We refer to findings from our reanalysis of Teixeira et al.'s [-@teixeira_white_2022] experiment in the main text.

>>>>

<!-- # Reanalysis of Teixeira et al.'s [-@teixeira_white_2022] experiment -->

<!-- At the height of the 2020 Black Lives Matter protests, @teixeira_white_2022 exposed White Americans ($N = 399$) to photos of either peaceful or destructive Black Lives Matter protests and asked them to rate how legitimate (i.e., fair, reasonable, legitimate, and justified) they thought the pictured protests were. As such, their findings make for an interesting comparison to our findings. @teixeira_white_2022, however, reported results from a linear model estimating the three-way interaction between the experimental manipulation, belief in systemic racial injustice, and group identification while controlling for political orientation. This analysis did not provide a direct comparison to our findings.  -->

<!-- To compare theirs to our findings, we instead estimated a series of simpler linear regression models, using the brms R package [@burkner_brms_2017; @burkner_advanced_2018] and weakly informative Student-*t* $(3, 0, 2.5)$ prior distributions, with participants' ratings of how legitimate the pictured protests were as the outcome variable.^[We thank the authors for making their data available online ([https://osf.io/sud2y/](https://osf.io/sud2y/)).] First, we found that, as expected, participants considered peaceful protests far more legitimate than destructive protests ($\text{Cohen's}~d = 1.14, [0.98, 1.30]$). Second, we found that more conservative participants rated destructive protests ($\beta_{xy} = -0.59, [-0.68, -0.49]$) and, to a lesser extent, peaceful protests ($\beta_{xy} = -0.20, [-0.30, -0.10]$) to be less legitimate than more liberal participants. Third, we found that participants who identified more strongly with their (White American) ethnic identity rated destructive protests ($\beta_{xy} = -0.35, [-0.45, -0.24]$) and, to a lesser extent, peaceful protests ($\beta_{xy} = -0.10, [-0.21, 0.01]$) to be less legitimate than participants who identified less strongly with their (White American) ethnic identity. Finally, we found that participants' group identification was no longer associated with how legitimate they rated peaceful ($\beta_{xy} = -0.02, [-0.13, 0.05]$) and destructive ($\beta_{xy} = -0.06, [-0.17, 0.05]$) protests to be after controlling for their political orientation. We refer to findings from our reanalysis of Teixeira et al.'s [-@teixeira_white_2022] experiment in the main text. -->
